\documentclass[12pt]{article}

\begin{document}

\begin{center}
{\Huge \textbf{Snapshot Objectives}}\\[0.5cm]
{\large Parks and Recreation Mobile App Enhancement}\\[0.3cm]
{\large December 2025}
\end{center}

\section*{1. Start Objective (Snapshot 1)}
The goal of the project start was to establish the core foundation of the application.  
This included:
\begin{itemize}
    \item Defining the project scope and objectives.
    \item Setting up the framework and development environment using React Native and Expo.
    \item Establishing the base architecture (map, home screen, navigation structure).
    \item Delegating tasks among team members.
    \item Identifying initial dependencies such as react-native-maps and Expo libraries.
\end{itemize}
The main purpose of this snapshot was to create a functional base that future features could be built upon.

\section*{2. Checkpoint 1 Objective (Snapshot 2)}
This checkpoint reflects progress from the initial phase and introduces the first major feature addition.
\subsection*{Reflection}
\begin{itemize}
    \item Core application screens were established (Home Screen, Map, Backpack).
    \item Navigation between screens was implemented.
    \item Initial geolocation functionality was integrated.
\end{itemize}

\subsection*{New Tasks Added}
\begin{itemize}
    \item Implementation of the \textbf{Exercise Module} (squat detection using the barometer).
    \item Add new dependencies such as Expo-Barometer.
    \item Update UI design and screen flow to include exercise triggers.
    \item Update SDD, SRS, and workflow diagrams to reflect the new module.
    \item Add initial TestRail test cases for the new module.
\end{itemize}

\section*{3. Checkpoint 2 Objective (Snapshot 3)}
This checkpoint involved reflecting on the previous additions and expanding the app with another major feature.

\subsection*{Reflection}
\begin{itemize}
    \item Exercise module completed and integrated with reward flow.
    \item UI for quizzes, backpack, and pet selection refined.
    \item Architecture updated to support multiple mini-games.
\end{itemize}

\subsection*{New Tasks Added}
\begin{itemize}
    \item Add \textbf{Camo Module} (find-the-hidden-animal mini-game).
    \item Add \textbf{Predator Module} (step-based escape event).
    \item Update workflow and DFD diagrams to include both modules.
    \item Add new dependencies if needed (e.g., image-handling utilities).
    \item Expand TestRail test plans for new modules.
\end{itemize}

\section*{4. Final Due Date Checkpoint (Snapshot 4)}
This final snapshot summarizes completed work and identifies potential future enhancements.

\subsection*{Reflection}
\begin{itemize}
    \item All major modules completed (Exercise, Quiz, Camo, Predator, Carousel).
    \item UI flow refined and cleaned.
    \item Pet system and health bar fully integrated.
    \item Documentation updated (SDD, SRS, UI flows, references).
    \item Final TestRail execution and test results added.
\end{itemize}

\subsection*{Future Work}
\begin{itemize}
    \item Improve squat detection accuracy.
    \item Add more quizzes, animations, or additional pets.
    \item Improve predator logic and add more variations.
    \item Implement cloud-based user profiles.
    \item Enhance accessibility features and voice interactions.
\end{itemize}

\end{document}
