\documentclass[12pt]{article}

% Packages
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{fancyhdr}

% Page Layout
\geometry{a4paper, margin=1in}

\pagestyle{fancy}
\fancyhead[L]{Parks and Recreation Mobile App Enhancement}
\fancyhead[R]{Page \thepage}

\begin{document}

\title{Project Design Specification:\\ Parks and Recreation Mobile App Enhancement}
\author{Prepared by: Alejandro Perez, Matthew Floresca Tom, Jason Giang, Jayden Darling\\ Los Angeles Parks and Recreation Department}
\date{Version 1.0, December 11, 2025}
\maketitle

\newpage

\section*{1. Overview}
The app enhances user engagement with LA County Parks through gamification, geolocation, and interactive features. It includes a treasure-hunt style game, educational quizzes, and fitness tracking for children and families.

\section*{2. Design Goals}
\begin{itemize}
    \item Cross-platform (iOS and Android)
    \item Geolocation and motion detection
    \item Gamification: virtual pets, quizzes, treasure hunts
    \item Accessibility: text-to-speech, offline functionality
    \item Performance and data security optimization
\end{itemize}

\section*{3. System Architecture}
The system follows a client-server model, consisting of the following components:
\begin{itemize}
    \item \textbf{Mobile App}: User interface, game mechanics, geolocation, and motion detection.
    \item \textbf{Backend Services}: API server, database, analytics, and file server.
\end{itemize}

\section*{4. Core Features}
\subsection*{Main Screen}
\begin{itemize}
    \item Interactive map with Points of Interest (POIs), pet status, and proximity detection.
    \item Quick access to pet health, steps counter, and inventory.
\end{itemize}

\subsection*{Pet Management}
\begin{itemize}
    \item Virtual pets with health tracking, food/water levels, and replenishment.
\end{itemize}

\subsection*{Gamification}
\begin{itemize}
    \item \textbf{Quiz Module}: Park-related trivia with rewards.
    \item \textbf{Exercise Module}: Motion-based tracking and rewards.
    \item \textbf{Camouflage Module}: Geolocation-based hide-and-seek with animals.
\end{itemize}

\subsection*{Inventory Management}
\begin{itemize}
    \item Item collection, usage for pet health restoration, and capacity tracking.
\end{itemize}

\subsection*{Geolocation \& Motion Detection}
\begin{itemize}
    \item GPS-based location tracking with fallback for network-based location.
    \item Step counting, exercise tracking, and feedback.
\end{itemize}

\subsection*{Accessibility}
\begin{itemize}
    \item Text-to-speech and offline functionality for users without internet.
\end{itemize}

\section*{5. User Interface Design}
\subsection*{Screens}
\begin{itemize}
    \item Splash/Login, Home, Pet Selection, Quiz, Exercise, Camo, Backpack, Settings, POI Info.
\end{itemize}

\subsection*{Design Principles}
\begin{itemize}
    \item \textbf{Child-Friendly}: Large touch targets, bright colors, simple navigation.
    \item \textbf{Intuitive}: Minimal text, consistent iconography, visual feedback.
    \item \textbf{Performance-Optimized}: Quick transitions, smooth animations, minimal latency.
    \item \textbf{Accessible}: Support for text scaling, high contrast modes, screen readers.
\end{itemize}

\section*{6. Technology Stack}
\subsection*{Frontend}
\begin{itemize}
    \item \textbf{iOS}: Swift (SwiftUI/UIKit).
    \item \textbf{Android}: Kotlin (Android Jetpack).
    \item \textbf{Cross-Platform Assets}: React Native/Flutter (optional).
\end{itemize}

\subsection*{Backend}
\begin{itemize}
    \item \textbf{Runtime}: Node.js/Python (Django/Flask).
    \item \textbf{API}: Express.js.
    \item \textbf{Database}: MongoDB.
    \item \textbf{Authentication}: JWT.
\end{itemize}

\section*{7. Security}
\begin{itemize}
    \item \textbf{Data Encryption}: HTTPS, AES-256.
    \item \textbf{Authentication}: OAuth 2.0 with JWT.
    \item \textbf{Compliance}: COPPA for children's data protection.
\end{itemize}

\section*{8. Testing and Performance}
\subsection*{Testing}
\begin{itemize}
    \item Unit, integration, and user acceptance testing.
\end{itemize}

\subsection*{Performance}
\begin{itemize}
    \item Optimized for quick load times, minimal battery use, and smooth animations.
\end{itemize}

\section*{9. Deployment and Maintenance}
\begin{itemize}
    \item \textbf{Beta Testing}: Gradual public rollout.
    \item \textbf{Updates}: Regular bug fixes, feature enhancements, and security patches.
\end{itemize}

\section*{10. Risk Analysis}
\subsection*{Technical Risks}
\begin{itemize}
    \item GPS inaccuracies, battery drain, network issues, and cross-platform compatibility.
\end{itemize}

\subsection*{Operational Risks}
\begin{itemize}
    \item Server downtime, scalability issues, and data privacy violations.
\end{itemize}

\end{document}
